---
title: "Example RevealJS Slides"
subtitle: "Let's Rock and Roll!"
date: now
author:
  - name: FirstName LastName
    email: person@stanford.edu
format:
  stanford-revealjs: default
---

## Welcome to the presentation.

Some quick house keeping notes for those new to RevealJS

### Navigation With keyboards

To move between slides in the presentation, please use: 

- next slide: spacebar, `j`, or right arrow
- previous slide: `k` or left arrow

## RevealJS Tools

Some other common tasks with RevealJS:

- menu bar for options: `m`
- overview of slides: `o`
- zoom element: `alt` (windows) or `option` (mac)
- [print slides](https://quarto.org/docs/presentations/revealjs/presenting.html#print-to-pdf)

## Chalkboard

This slide theme using [reveal-js.calkboard](https://github.com/rajgoel/reveal.js-plugins/tree/master/chalkboard) plugin to allow for annotations. See [Quarto documentation](https://quarto.org/docs/presentations/revealjs/presenting.html#chalkboard) for supported options. Note, the following keyboard short cuts:

- notes: `c`
- chalkboard: `b`
- delete drawing: `del`
- download drawing: `d`


## Slide with some mathematics

Display: 

$$a^2 = b^2 + c^2$$

Inline: $\frac{a+b}{a} = \frac{a}{b} = \varphi$

## Slide with lists that increment

Below is a list that as you move forward the items are displayed. 

::: {.incremental}
- Hello there!
  1. Yogurt
  2. Flank steak
- Goodbye! 
:::


## Some quick R

Example R code:

```{r}
1 + 1
```

```{r}
plot(pressure)
```
