---
title: "Example HTML Page"
subtitle: "Let's rock and roll!"
date: now
author:
  - name: FirstName LastName
    email: person@stanford.edu
format:
  stanford-html: default
---

```{r}
#| label: load-packages
#| echo: false

library(ggplot2)
data(mpg, package = "ggplot2")
```

Consider the `mpg` data set found in the `ggplot2` package. In this data set, there are `{r} nrow(mpg)` observations and `{r} ncol(mpg)` variables.

The plots in @fig-mpg show the relationship between city and highway mileage for 38 popular models of cars.
In @fig-mpg-1 the points are colored by the number of cylinders while in @fig-mpg-2 the points are colored by engine displacement.

```{r}
#| label: fig-mpg
#| fig-cap: "City and highway mileage for 38 popular models of cars."
#| fig-subcap:
#|   - "Color by number of cylinders"
#|   - "Color by engine displacement, in liters"
#| layout-ncol: 2
#| column: page
#| cache: true

ggplot(mpg, aes(x = hwy, y = cty, color = cyl)) +
  geom_point(alpha = 0.5, size = 2) +
  scale_color_viridis_c() +
  theme_minimal()

ggplot(mpg, aes(x = hwy, y = cty, color = displ)) +
  geom_point(alpha = 0.5, size = 2) +
  scale_color_viridis_c(option = "E") +
  theme_minimal()
```

Example mirrored from: 

<https://quarto.org/docs/get-started/computations/rstudio.html#multiple-figures>